---
title: "linear models"
author: "Kevin Cunningham"
date: "7/1/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---



```{r}
quantile_df <- read.csv("/Users/Kevin/Desktop/Grad school docs and past classes/New_RA_Project_code/PCA/after_quantile_reduced_set.csv")
```

order the data by sample status
```{r}
quantile_df <- quantile_df[order(quantile_df$Sample_Status),]
```

Add a feature for the sample status. If RA the value will be 1, if control the value will be 0
```{r}
quantile_df$Sample_Status_as_numeric <- 1
```

Last 30 samples need to be changed to 0, all RA is given the value of 1
```{r}
for (i in 65:94) {
  quantile_df[i,1625] <- 0
}
#View(quantile_df)
```

make a dataframe to hold the p values and add the feature names
```{r}
logistic_regression_pvalues <- as.data.frame(matrix(data = 0, nrow = 1622, ncol = 2))
logistic_regression_pvalues$V1 <- feature_names
colnames(logistic_regression_pvalues) <- cbind("Auto-antibody", "P-value")
#View(logistic_regression_pvalues)
```

fill the dataframe with the p values
```{r}
for (i in 1:1622) {
  glm_results <- glm(Sample_Status_as_numeric ~ quantile_df[,i], data = quantile_df, family = "binomial")
  pvalue_to_add <- coef(summary(glm_results))[2,4]
  logistic_regression_pvalues[i,2] <- pvalue_to_add
}
```

```{r}
coef(summary(glm_results))
print(pvalue_to_add)
```

Sort by p value
```{r}
logistic_regression_pvalues <- logistic_regression_pvalues[order(logistic_regression_pvalues$`P-value`),]
```

Find how many have a p value less than 0.05
```{r}
for(i in 1:1622){
  current_val3 <- logistic_regression_pvalues[i,2]
  if(current_val3 > 0.05){
    print(i)
    print("p value is larger than 0.05")
    break;
  }
}
```

```{r}
print(logistic_regression_pvalues[67,1])
print(logistic_regression_pvalues[67,2])
```

So there are 66 autoantibodies with p values less than 0.05
```{r}
logistic_regression_pvalues_less_than_05 <- logistic_regression_pvalues[1:66,]
#View(logistic_regression_pvalues_less_than_05)
```

When gathering all features, be sure to get all features from both RA and Control together. The final matrix should be
94 X 68
66 features, sample status, case ids
Have the data sorted by sample status and add the 
sample status and case id to the final dataframe for later use.
```{r}
ordered_quantile_df <- quantile_df[order(quantile_df$Sample_Status),]
```

Get the names of all features
```{r}
quantile_no_labels_df <- as.data.frame(quantile_df[,1:1622])
#View(quantile_no_labels_df)
feature_names <- colnames(quantile_no_labels_df)
#View(feature_names)
```

Gather all the features
```{r}
number_of_features_to_plot <- 66
#make a dataframe to hold the names of the features we need
top_feature_names_to_add <- as.data.frame(matrix(data = 0, nrow = 1, ncol = number_of_features_to_plot))
for(i in 1:number_of_features_to_plot){
  feature_to_add <- logistic_regression_pvalues_less_than_05[i,1]
  #print(feature_to_add)
  top_feature_names_to_add[1,i] <- feature_to_add
}
#View(top_feature_names_to_add)
#make a dataframe to hold the features
logistic_regression_features <- as.data.frame(matrix(data = 0, nrow = 94, ncol = number_of_features_to_plot))
colnames(logistic_regression_features) <- cbind(top_feature_names_to_add)
#View(logistic_regression_features)
logistic_regression_features$Sample_Status <- ordered_quantile_df$Sample_Status
logistic_regression_features$Case_ID <- ordered_quantile_df$Case_ID
feature_values_to_add <- matrix(data = 0, nrow = 94, ncol = 1)
feature_names_as_column <- t(feature_names)
feature_count = 1
#View(feature_names_as_row)
for(a in (1:number_of_features_to_plot)){
  current_feature_to_find <- top_feature_names_to_add[1,a]  
  for(i in (1:1622)){
  feature_to_check <- feature_names_as_columnD[1,i]
    if(current_feature_to_find == feature_to_check){
      #print(current_feature_to_find)
      #print(feature_to_check)
      feature_values_to_add <- ordered_quantile_df[1:94,i]
      #View(feature_values_to_add)
      logistic_regression_features[1:94,feature_count] <- feature_values_to_add
      feature_count = feature_count + 1
    }
  }
}
#View(logistic_regression_features)
```

The 66 features plus the sample status and case id is in the
dataframe "logistic_regression_features" for all 94 samples.













